Accelerated oblique random survival forests

### 2022-06-12 docs/index.Rmd
up to 25 slides

---
title: "Accelerated oblique random survival forests"
author: "Byron C. Jaeger"
date: Last updated `r Sys.Date()`
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle
background-image: url("img/meme_slow_R.jpg")
background-size: contain

@@

library(tidyverse)
library(ggforce)
library(rpart)
library(rpart.plot)
library(party)
library(parttree)
library(palmerpenguins)
library(gt)
library(table.glue)
library(xaringanExtra)

# infinite moon reader doesn't like targets,
# this commented code sets up files that work for infinite moon reader
# tar_load(
#   names = c(
#     bm_pred_model_viz,
#     bm_pred_time_viz,
#     bm_pred_viz,
#     data_key
#   )
# )
# 
# write_rds(bm_pred_model_viz, "docs/index_files/bm_pred_model_viz.rds")
# write_rds(bm_pred_time_viz, "docs/index_files/bm_pred_time_viz.rds")
# write_rds(bm_pred_viz, "docs/index_files/bm_pred_viz.rds")
# write_rds(data_key, "docs/index_files/data_key.rds")

bm_pred_model_viz <- read_rds('index_files/bm_pred_model_viz.rds')
bm_pred_time_viz <- read_rds('index_files/bm_pred_time_viz.rds')
bm_pred_viz <- read_rds('index_files/bm_pred_viz.rds')
data_key <- read_rds('index_files/data_key.rds')

@@

##

@@

@@

@@

---
## Data sets contd.

@@

## Data sets contd.

@@

```{r bm_pred_time_viz, fig.height=6.5, fig.width=8}
bm_pred_time_viz
```

>>>>

---
title: "Accelerated oblique random survival forests"
author: "Byron C. Jaeger"
date: Last updated `r Sys.Date()`
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

library(tidyverse)
library(ggforce)
library(rpart)
library(rpart.plot)
library(party)
library(parttree)
library(palmerpenguins)
library(gt)
library(table.glue)

tar_load(
  names = c(
    bm_pred_model_viz,
    bm_pred_time_viz,
    bm_pred_viz,
    data_key
  )
)

@@

@@

Jaeger showed in general benchmarks that the oblique RSF had higher prediction accuracy than axis-based RSFs. However, the obliqueRSF R package is hundreds of times slower than standard R packages for axis based RSFs.

@@

---
class: center, middle
background-image: url("img/meme_slow_R.jpg")
background-size: contain

@@

---
## Data sets continued

@@

## Data sets continued

@@

```{r bm_pred_time_ridges, fig.height=6.5, fig.width=8}
bm_pred_time_viz
```
